### 2018-02-11 submission/manuscript.Rmd
spiffy up the conclusion section

By aggregating together a large collection of studies analyzing both fecal and colon tissue samples, we are able to provide evidence supporting the importance of the bacterial community in colorectal tumors. Further, the data presented here suggests that mouth-associated microbes can gain a foothold within the colon and are commonly associated with the greatest OR of individuals having a carcinoma. No conclusive signal with these mouth-associated microbes could be detected for adenoma stage of disease. Our observations also highlight the importance of power and sample number considerations when investigating the microbiota and adenoma stage of disease due to possible subtle changes in the community. Overall, associations between the microbiota and individuals with carcinoma stage of disease were much stronger than with to those with adenoma stage of disease.

>>>>

By aggregating together a large collection of studies analyzing both fecal and colon tissue samples, we are able to provide evidence supporting the importance of the bacterial community in colorectal tumors. The data presented here suggests that mouth-associated microbes can gain a foothold within the colon and are commonly associated with the greatest OR of individuals having a carcinoma. Conversely, no conclusive signal with these mouth-associated microbes could be detected for individuals with an adenoma. Our observations also highlight the importance of power and sample number considerations when investigating the microbiota and adenoma tumors due to possible subtle changes in the community. Overall, associations between the microbiota and individuals with carcinomas were much stronger than with those with adenomas.
